\text{Additive drift with tail bounds}

### 2021-08-26 article.tex
add some sections

\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage[utf8]{inputenc}
\usepackage[english,russian]{babel}
\usepackage{indentfirst}
\usepackage{graphicx}
\usepackage{mathtext}
\usepackage[T1,T2A]{fontenc}
\usepackage{listings}
\usepackage{hyperref}
\usepackage{stmaryrd}

@@

\title{\text{Limits}}
\date{04-08-2021}
\author{\text{Vihnin F.}}

@@

\newcommand{\expx}[1]{e^{-|x|^{#1}}}
\newcommand{\expxpoz}[1]{e^{-x^{#1}}}
\newcommand{\infint}[1]{\int_{-\infty}^{+\infty} #1 \, dx}
\newcommand{\infintpoz}[1]{\int_{0}^{+\infty} #1 \, dx}

@@

\begin{document}
\maketitle
\newpage

\section*{Оценки на матожидание}

@@

\subsection*{Непрерывный случай}

@@

\subsection*{Дискретный случай}

@@

\section*{Случай 0-ого матожидания}
\label{sec:zero}

@@

\subsection*{Экспоненты от степеней икса}

@@

\section*{Заключение}

@@

\end{document}

>>>>

\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage{indentfirst}
\usepackage{graphicx}
\usepackage{mathtext}
\usepackage[T1,T2A]{fontenc}
\usepackage{listings}
\usepackage{hyperref}
\usepackage{stmaryrd}
\usepackage{a4wide}

@@

\title{\text{Additive drift with tail bounds}}

% \date{04-08-2021}

@@

\newcommand{\expx}[1]{e^{-|x|^{#1}}}
\newcommand{\expxpoz}[1]{e^{-x^{#1}}}
\newcommand{\infint}[1]{\int_{-\infty}^{+\infty} #1 \, dx}
\newcommand{\infintpoz}[1]{\int_{0}^{+\infty} #1 \, dx}
\newcommand{\cm}{coming soon\dots}

@@

\author{Vihnin F.
    \and Antipov D.
    \and Sinyachenko N.}

\begin{document}
\maketitle

\section{Introduction}
\cm

\section{Existing tools}
\cm
\subsection{Negative drift}
\begin{theorem}[Drift Theorem for Lower Bounds] \label{thm:neat}
    Let $\{X_t\}_{t \ge 0}$ be a Markow process over a set of states $\mathbb{S}$, and $\mathbf{g} : \mathbb{S} \rightarrow \mathbb{R}$ a function that assigns to every state a non-negative real numbers. Pick two real numbers $a(l)$ and $b(l)$ which depend on a parameter $l \in \mathbb{R}^+$ such that $0 < a(l) < b(l)$ holds and let the random variable $T$ denote
    the earliest point in time $t \ge 0$ where $\mathbf{g}(X_t) \leq a(l)$ holds.

    If there are constants $\lambda > 0$ and $D \ge 1$ and a polynomial $p(l)$ taking only positive values, for which the following four conditions hold

    \begin{enumerate}
        \item $\gfun(X_0) \ge b(l)$
        \item $\forall t \ge 0 : E[e^{-\lambda(\gfun(X_{t + 1} - \gfun(X_t)))} |\ X_t,\ \gfun(X_t) < b(l)] \leq 1 - \frac{1}{p(l)} = \rho$
        \item $\forall t \ge 0 : E[e^{-\lambda(\gfun(X_{t + 1} - b(l)))} |\ X_t,\ \gfun(X_t) \ge b(l)] \leq D$
    \end{enumerate}
    then for all time bounds $B \ge 0$, the following upper bound on probability for random variable $T$:

    \begin{equation}
        \Pr[T \leq B] \leq e^{\lambda(a(l) - b(l))} \cdot B \cdot D \cdot p(l)
    \end{equation}
\end{theorem}

To prove this theorem we need to use following lemma

\begin{lemma}[Hajek lemma 2.8] \label{lm:haj}
    If conditions 2 and 3 are met, then

    $$\forall t \ge 0 :\Pr[\gfun(X_t) \leq a(l)] \leq \rho^te^{\lambda(a(l) - \gfun(X_0))} + \frac{1 - \rho^t}{1 - \rho} D e^{\lambda(a(l) - b(l))}$$

\end{lemma}

\begin{proof}[Proof of Theorem \ref{thm:neat}]

    First of all we need to describe fact that time $T$ is less or equals $B$. It means that at any time $t \leq B$  event $\gfun(X_t) \leq a$ could have happened for first time, then

    % \[
    %     \Pr[T \leq B] = \sum_{k=1}^{B} \Pr[\gfun(X_k) \leq a \land \gfun(X_{k - 1}) > a \land ... \land \gfun(X_0) > a)] 
    % \]

    \begin{align*}
        \Pr[T \leq B] &= \sum_{k=1}^{B} \Pr[T = k] \\
        &= \sum_{k=1}^{B} \Pr[\gfun(X_k) \leq a \land \gfun(X_{k - 1}) > a \land ... \land \gfun(X_0) > a)] \\
        & \leq \sum_{k=1}^{B} \Pr[\gfun(X_k) \leq a]
    \end{align*}

        By Lemma $\ref{lm:haj}$:

    \begin{align*}
        \Pr[T \leq B] & \leq \sum_{k=1}^{B} \rho^k e^{\lambda(a(l) - \gfun(X_0))} + \frac{1 - \rho^k}{1 - \rho} D e^{\lambda(a(l) - b(l))}\\
        & = \rho \frac{1 - \rho^B}{1 - \rho} e^{\lambda a(l)}(e^{-\lambda\gfun(X_0)} - \frac{D}{1 - \rho} e^{-\lambda b(l)}) + e^{\lambda(a(l) - b(l))} \frac{B D}{1 - \rho}
    \end{align*}

    Because $\gfun(X_0) \ge b(l)$:

    \begin{align*}
        \Pr[T \leq B] & \leq \rho \frac{1 - \rho^B}{1 - \rho} e^{\lambda (a(l) - b(l))}(1 - \frac{D}{1 - \rho}) + e^{\lambda(a(l) - b(l))} \frac{B D}{1 - \rho}
    \end{align*}

    Then because $\frac{D}{1 - \rho} \ge 1 $:
    \begin{align*}
        \Pr[T \leq B] & \leq e^{\lambda(a(l) - b(l))} \frac{B D}{1 - \rho}\\
        & = e^{\lambda(a(l) - b(l))} \cdot B \cdot D \cdot p(l)
    \end{align*}

    Finally

    $$\Pr[T \leq B] \leq e^{\lambda(a(l) - b(l))} \cdot B \cdot D \cdot p(l)$$

\end{proof}
\subsection{Theorem for sub-gaussian processes}
\cm
\subsection{Comparing requirements}
\cm
\subsection*{Оценки на матожидание}

@@

\subsubsection*{Непрерывный случай}

@@

\subsubsection*{Дискретный случай}

@@

\subsection*{Случай 0-ого матожидания}
\label{sec:zero}

@@

\subsubsection*{Экспоненты от степеней икса}

@@

\subsection*{Заключение}

@@

\section{Tail bounds}
\cm
\section{Time bounds for process with variable $\lambda$}
\cm

\section{Conclusion}
\cm
\end{document}
